\textsf{Are frontier models superhuman chemists?}

### 2024-03-12 src/tex/ms.tex
add caching

\paragraph{\enquote{Tiny} subset}
It is important to note that for routine evaluations, a smaller subset of the corpus might be more practical.\cite{polo2024tinybenchmarks}
For instance,~\citet{liang2023holistic} report costs of more than 10,000 USD for \gls{api} calls for a single evaluation on the \gls{helm} benchmark on a model. 
To address this, we also provide a subset (\variable{output/num_tiny_questions.txt} questions) of the corpus that was curated to be a diverse and representative subset of the full corpus (see \Cref{sec:subset-selection} for details on the curation process).
We also used this subset to seed the app we used for the human baseline study. The results shown in the main text are based on this subset. 
Results for the full corpus can be found in the appendix.

@@

@@

\paragraph{Models}
\subparagraph{Completion models}
\texttt{Galactica-120b}\cite{taylor2022galactica}

@@

\paragraph{Participants}
Users were open to report about their experience in chemistry. 
\variable{output/num_users_with_education_info.txt} did so. 
Out of those, \variable{output/num_human_phd.txt} reported to have been awarded a Ph.D.
\variable{output/num_human_postdoc.txt} are beyond a first postdoc, \variable{output/num_human_master.txt} have a master's degree, and \variable{output/num_human_bachelor.txt} have a bachelor's degree and for \variable{output/num_human_highschool.txt} the highest awarded degree is from high school.

>>>>

\paragraph{\enquote{Tiny} subset}
It is important to note that for routine evaluations, a smaller subset of the corpus might be more practical.\cite{polo2024tinybenchmarks}
For instance,~\citet{liang2023holistic} report costs of more than 10,000 USD for \gls{api} calls for a single evaluation on the \gls{helm} benchmark on a model. 
To address this, we also provide a subset (\variable{output/num_tiny_questions.txt} questions) of the corpus that was curated to be a diverse and representative subset of the full corpus (see \Cref{sec:subset-selection} for details on the curation process).
We also used this subset to seed the app we used for the human baseline study.

@@

%% Note also while the performance of the systems is better than what humans do, it is still far from perfect

@@

\paragraph{Models}
\subparagraph{Completion models}
We used \texttt{Galactica-120b}\cite{taylor2022galactica} with the default settings

@@

\paragraph{Participants}
Users were open to report about their experience in chemistry. 
Overall, \variable{output/num_users_with_education_info.txt} did so. 
Out of those, \variable{output/num_human_phd.txt} reported to have been awarded a Ph.D.
\variable{output/num_human_postdoc.txt} are beyond a first postdoc, \variable{output/num_human_master.txt} have a master's degree, and \variable{output/num_human_bachelor.txt} have a bachelor's degree and for \variable{output/num_human_highschool.txt} the highest awarded degree is from high school.

\paragraph{Comparison with models}
To compare the performance of humans (who might have answered only some questions) with the performance of models (which answered all questions), we focussed on questions which at least four humans answered and limited the pool of human scorers to those who answered at least 100 questions (i.e., \variable{output/num_humans_with_more_than_100_scores.txt} humans). 
The latter threshold was chosen to limit it to humans who made serious attempts at systematically answering a part of the questions. 
This analysis might lead to potential biases, most likely in favor of humans as they were allowed to skip questions. \variable{output/num_humans_with_204_scores.txt} humans answered more than 200 questions.
